Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
- size ratio discussion
conclusion initial draft

\section{Experimental C-space size gain of asynchronous systems}
	One of the advantages of asynchronous systems over synchronous systems in the
	context of periodic tasks is that the critical instants of asynchronous systems
	cannot be more constraining for the C-space than synchronous instants. For this
	reason, it has long been known that modifying task offsets when possible during
	the design of a real-time system is a useful trick to fit a heavy but periodic task set
	into a given platform.

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets without
	synchronous instants were generated and the size of their C-space was
	calculated and compared with the size of the C-space of the same
	task sets with all task offsets set to zero. In other words, this figure
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.5\textwidth]{figs/sizeRatio.png}
			\caption{C-space size ratio between asynchronous and equivalent synchronous
			systems}
			\label{fig:sizeRatio}
		\end{center}
	\end{figure}

@@

>>>>

@@

In this paper, we presented a general approach to define the C-space of a constrained periodic task set for EDF on uniform platform. Possible future works includes an extension to multiprocessor platforms or including preemption costs, in which case EDF is no longer an optimal algorithm, meaning that another algorithm could be studied.

(...)
